%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Aidan}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Mongan}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Computer Science Graduate} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Dublin, Ireland}\\
	\icon{MapMarker}{12}{Clonskeagh}\\
	\icon{Phone}{12}{+353 85 176 7977}\\
	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	%\icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	\icon{Github}{12}{\href{https://github.com/alyxvance}{github.com/monganai}}\\
	\icon{At}{12}{\href{mailto:alyx@vance.me}{monganai@tcd.ie}}\\	
	%\icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.45\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	A recent computer science graduate with well developed communication, cooperation, and leadership skills from both leading and participating in many
group projects throughout college. 
working part-time resulted in exelent punctuality and timekeeping which has been
demonstrated throughout my academic and working
career. With 40 hour college weeks, my ability to work
under pressure is strong.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.45\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
\baritem{Java}{100}
		
		
		\baritem{C++}{80}
		\baritem{Microprocessors}{70}
\baritem{Python}{60}
		\baritem{Git}{55}
		\baritem{Scalable Computing}{45}
		\baritem{LaTeX}{40}

	\end{barchart}
\end{minipage}

%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{8/2015 -- 2019}
		{Customer Sales Advisor -> Bicycle Technician}
		{Halfords}
		{Working throughout college, and initially starting part time as a sales representative, my most
recent role was a bicycle technician specializing in diagnosing and repairing electric bicycles.
 \texttt{Electronics}\slashsep\texttt{Teamwork}\slashsep\texttt{Communication Skills}}
	
\end{entrylist}



%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2008 -- 2014}
		{Leaving Certificate}
		{St Benildus College}
		{Completed Leaving certificate in 2014, achieving 460 CAO points, Achieving my top marks in Honours Maths \& Design Communication Graphics.}

	\entry
		{2014 -- 2019}
		{B. A (mod) Computer Science}
		{Trinity College Dublin}
		{2.1 overall while achieving a first class honours in final year, Modules ranging from implementing logic gates in software to complex computer vision applications.}
	
\end{entrylist}






%----------------------------------------------------------------------------------------
%	Academiec achievements
%----------------------------------------------------------------------------------------

\cvsect{Academic Achievements}

\begin{entrylist}
	\entry
		{2019}
		{Group Project - Winner}
		{Trinity College Dublin}
		{Head of hardware for project "IncuBetter", A standalone smart incubator designed for Médecins Sans Frontières (MSF)   \texttt{Python}\slashsep\texttt{openCV}\slashsep\texttt{Linux}\slashsep\texttt{Raspberry Pi} \slashsep\texttt{custom circuitry}}


	\entry
		{2019}
		{Best Dissertation Pitch}
		{Trinity College Dublin}
		{Best presentation pitch of computer science 2019 regarding dissertation project "RideSafe"  \texttt{Android Studio}\slashsep\texttt{LaTex}\slashsep\texttt{Java}\slashsep\texttt{XML}\slashsep\texttt{Git}}
	
\end{entrylist}



%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.15\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - native\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}

Technology has been of an interest since I was
a child, nowadays I like to keep up to date with
the cutting edge of both hardware and software
reading articles online. practical activities include hardware repair/modifications for items
around the house as well as for others.
Expanding on my study of microprocessors in
college I self taught soldering and some ba-
sic electronic components. Personal projects
range from the sound system and custom wire-
less charger built into my car to a working pro-
totype for "RippleSence" - winner of the Bolton
Trust (DIT 2017).

	
	
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\vspace{1.2cm}
	
	Cycling has always been a huge part of my life
in multiple ways. I have been an avid mountain
biker since 2008 - In the early days I kept de-
stroying my bike, having no income I self taught
bicycle repair which ultimately led to my role at
Halfords. My time off is generally spent at one
of the local trail centres when the weather per-
mitts.


Fishkeeping is my most recent hobby, currently
limited to two aquaria in my home I enjoy the
challenging aspect of maintaining both tropical
and marine mini-ecosystems as healthy as pos-
sible.

\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
